---
title: "Alternative Final Exercise"
output:
  word_document: default
  html_notebook: default
---
Loading Libraries
```{r}
rm(list=ls())
library(haven)
library(readxl)
library(dplyr)
library(ggplot2)
library(plm)
```
Loading Data
```{r}
# Load in WDI Data
wdi.data <- read_dta("~/desktop/stats/final_exercise/wdi.dta")

# LOAD WDI COUNTRIES
wdi.countries <- read_excel("~/desktop/stats/final_exercise/FinalExercise/Country.xlsx")
```

```{r}
# Selected Attributes
wdi.selected <- select(wdi.data, countryname, countrycode, year, sp_ado_tfrt, se_sec_enrr, se_sec_enrr_fe, se_sec_enrr_ma, ny_gdp_pcap_cd, si_pov_gini, sp_pop_totl_fe_zs, se_com_durs, sp_dyn_conu_zs, sp_uwt_tfrt, sp_pop_totl, sh_sta_mmrt_ne, sp_rur_totl_zs, sl_tlf_0714_fe_zs, sl_tlf_acti_1524_fe_ne_zs, se_prm_enrr)

# Rename Columns
names(wdi.selected) <- c("Country_Name", "Country Code", "Year", "Adolescent_Fertility_Rate","Secondary_School_Enrollment", "Female_Secondary_School_Enrollment", "Male_Secondary_School_Enrollment", "GDP_Per_Capita", "GINI", "Percent_Female", "Compulsory_Education", "Contraceptive Prevalence", "Unmet Need for Contraception", "Population", "Maternal_Mortality_Rate", "Percent_Rural_Population", "Female_Child_Employment", "Female_Labor_Force_Participation", "Primary_School_Enrollment")

wdi.did <- filter(wdi.selected, (Country_Name =="Costa Rica" | Country_Name=="Peru") & (Year >= 1978 & Year <= 2014))

wdi.more <- filter(wdi.selected, (Country_Name =="Costa Rica" | Country_Name=="Peru" | Country_Name=="Panama" | Country_Name=="Guatemala" | Country_Name=="Honduras" | Country_Name=="Dominican Republic" | Country_Name=="Ecuador" | Country_Name=="Venezuela, RB" | Country_Name=="Colombia" | Country_Name=="Paraguay") & (Year >= 1978 & Year <= 2014))

ggplot(data=wdi.did)+ 
  geom_line(aes(`Year`, `Adolescent_Fertility_Rate`, group=`Country_Name`, colour=`Country_Name`),) +  
  ggtitle("Plot of Adolescent Fertility Rate by Year, Costa Rica & Peru") +
  geom_vline(xintercept = 1994)
```
Primary School Enrollment Regressions
```{r}
ggplot(data=wdi.did)+ 
  geom_line(aes(`Year`, `Primary_School_Enrollment`, group=`Country_Name`, colour=`Country_Name`),) +
  ggtitle("Plot of Primary School Enrollment by Year, Costa Rica & Peru") +
  geom_vline(xintercept = 1994)

ggplot(data=wdi.more)+ 
  geom_line(aes(`Year`, `Primary_School_Enrollment`, group=`Country_Name`, colour=`Country_Name`),) +
  ggtitle("Plot of Primary School Enrollment by Year, More") +
  geom_vline(xintercept = 1994)
```
Set up Diff-in-Diff Variables
```{r}
# Set "intervention"" variable for all observations after 1994
wdi.did$intervention <- ifelse(wdi.did$Year > 1994, 1, 0)
# Set "treated" for all treated countries (i.e. Costa Rica)
wdi.did$treated <- ifelse(wdi.did$Country_Name == "Costa Rica", 1, 0)
# Set up the interaction variable "did" to be intervention * treated
# In this case set 1 for observations of Costa Rica after 1994 when the intervention occured
wdi.did$did <- wdi.did$intervention * wdi.did$treated
```
Primary School Regressions
Regress Adolescent Fertility Rate on Primary School Enrollment
```{r}
# Regress Adolescent Fertility Rate on Primary School Enrollment
primarySchoolEnrollReg <- lm(data=wdi.did, Adolescent_Fertility_Rate ~ Primary_School_Enrollment + GDP_Per_Capita)

summary(primarySchoolEnrollReg)
```
Diff-in-Diff regression to show impact of intervention on Primary School Enrollment
First Stage Regression (see bottom for second stage regresssion)
```{r}
# Diff-in-Diff regression to show impact of intervention on Primary School Enrollment
# When you control for GDP_Per_Capita the significance disappears....
primaryDidReg <- lm(Primary_School_Enrollment ~ treated + intervention + did, data = wdi.did)

summary(primaryDidReg)
```
Secondary School Enrollment Charts
```{r}
ggplot(data=wdi.did)+ 
  geom_line(aes(`Year`, `Secondary_School_Enrollment`, group=`Country_Name`, colour=`Country_Name`),) +
  ggtitle("Plot of Secondary School Enrollment by Year, Costa Rica & Peru") +
  geom_vline(xintercept = 1994)
ggplot(data=wdi.more)+ 
  geom_line(aes(`Year`, `Secondary_School_Enrollment`, group=`Country_Name`, colour=`Country_Name`),) +
  ggtitle("Plot of Secondary School Enrollment by Year, More") +
  geom_vline(xintercept = 1994)
```
Secondary School Enrollment Regressions
Regress Adolescent Fertility Rate on Secondary School Enrollment
```{r}
secondarySchoolEnrollReg <- lm(data=wdi.did, Adolescent_Fertility_Rate ~ Secondary_School_Enrollment + GDP_Per_Capita)

summary(secondarySchoolEnrollReg)

```
First State Regression
Diff-in-Diff regression to show impact of intervention on the Secondary School Enrollment
```{r}

# Diff-in-Diff regression to show impact of intervention on Secondary School Enrollment
# When you control for GDP_Per_Capita the significance disappears....
secondaryDidReg <- lm(Secondary_School_Enrollment ~ treated + intervention + did, data = wdi.did)

summary(secondaryDidReg)
```
Second State Regression
Diff-in-Diff regression to show the impact of the intervention on the Adolescent Fertility Rate
```{r}
fertilityDidReg <- lm(Adolescent_Fertility_Rate ~ treated + intervention + did + GDP_Per_Capita, data = wdi.did)

summary(fertilityDidReg)
```


